---
params:
  audience: academia
format:
  pdf:
    toc: false
    number-sections: false
    colorlinks: true
    documentclass: scrartcl
    papersize: letter
    pdf-engine: xelatex
    fontsize: 10pt
    geometry:
      - margin=1in
      - heightrounded
    include-in-header:
      - preamble.tex
execute:
  warning: false
  echo: false
  message: false
  eval: true
---

```{r}
#| name: setup
#| include: false
#| message: false
#| warning: false
#| eval: true

knitr::opts_chunk$set(
  fig.path = "figs/",
  fig.width = 7.252,
  fig.height = 4,
  comment = "#>",
  fig.retina = 3
)

library(knitr)
library(dplyr)
library(stringr)
library(lubridate)
library(kableExtra)
source("functions.R")

escape_latex_text <- function(x) {
  x <- as.character(x)
  x <- stringr::str_replace_all(x, fixed("\\"), "\\\\textbackslash{}")
  x <- stringr::str_replace_all(x, "([#$%&_{}])", "\\\\\\1")
  x <- stringr::str_replace_all(x, fixed("~"), "\\\\textasciitilde{}")
  x <- stringr::str_replace_all(x, fixed("^"), "\\\\textasciicircum{}")
  x
}
```

\par\centering{\LARGE{Michael F. McCoy III}}
\par\centering{PhD Student in Translational Biomedical Sciences (Neuroscience)}
\vspace{-5pt}
\par\centering{Rowan University}
\vspace{-5pt}
\par\centering{Virtua Health College of Medicine \& Life Sciences}
\vspace{-5pt}
\par\centering{Stratford, NJ}
\vspace{-5pt}
\par\centering{{\large\Letter} mccoym43@rowan.edu}
\vspace{-5pt}
\par\centering{\href{https://www.linkedin.com/in/themichaelmccoy}{LinkedIn} | \href{https://github.com/mmccoy-01}{GitHub}}

\vspace{-10pt}

# Education

\vspace{-10pt}

\begin{longtable}{p{2.8cm} p{13cm}}

2025--Present &
\textbf{Ph.D. in Translational Biomedical Sciences (Neuroscience)}, Rowan University, Stratford, NJ \\[8pt]

2022 & \textbf{B.A. in Psychology}, Minor in Neuroscience, Honors Program, Arcadia University, Glenside, PA \\
     & \hspace{1.5em}Study Abroad, University of Stirling, Stirling, Scotland, UK (2019) \\

\end{longtable}

\vspace{-15pt}

# Research Interests
- Cancer immunotherapy and leukemia biology: cellular mechanisms underlying targeted therapies in B-ALL and T-ALL.

- Hedgehog signaling and sensory biology: signaling mechanisms in taste/tongue systems and epithelial-neural communication.

- Behavioral neuroscience: body perception, cognition, and rodent behavioral paradigms.

- Translational biomedical research: integrating wet-lab experimentation with computational research workflows and reproducible data tools.

\vspace{-15pt}

# Research Experience

\vspace{-10pt}

\begin{longtable}{p{2.8cm} p{13cm}}

2023--2025 &
\textbf{Research Technician III}, Children's Hospital of Philadelphia \\
& PI: David T. Teachey and Caroline J. Diorio \\
& Conducted survival and bioluminescent imaging studies to track progression of targeted B-cell and T-cell therapies in acute lymphoblastic leukemia using patient-derived xenograft models in immunocompromised mice. Developed interactive R Shiny / Quarto dashboards to document experimental workflows and monitor treatment efficacy and disease progression. \\[8pt]

2022--2023 &
\textbf{Laboratory Animal Caretaker}, Children's Hospital of Philadelphia, Department of Veterinary Resources \\
& Maintained AALAS and AAALAC standards for research animal care and husbandry, conducted daily welfare checks, and supported SOP/GLP-compliant animal facility operations involving mice, rats, sheep, and pigs. \\[8pt]

2020--2022 &
\textbf{Research Assistant}, Rodent Altruism and Psycho-Pharmacology Lab, Arcadia University \\
& PI: Logan J. Fields and Juan F. Duque \\
& Administered oral cannabidiol treatments in rodent models of early-life stress, developed SOPs for open field and novel object recognition tasks, and contributed to IACUC protocol development and approval. \\[8pt]

2020 &
\textbf{Animal Care Staff}, Arcadia University \\
& Provided hands-on husbandry for laboratory rats, including handling, bedding changes, weighing, and feeding. \\

\end{longtable}

\vspace{-15pt}

# Publications
<!-- Set spacing in between list -->
\apptocmd{\tightlist}{\setlength{\itemsep}{4pt}}{}{}

```{r}
pubs <- get_cv_sheet("pubs") %>%
  mutate(
    year_num = year,
    year = ifelse(is.na(year), "", paste0("(", year, ")")),
    journal = ifelse(is.na(journal), "", paste0("_", journal, "_")),
    number = ifelse(is.na(number), "", paste0(number, ".")),
    doi = ifelse(
      is.na(doi) | doi == "",
      "",
      paste0("DOI: [", doi, "](https://doi.org/", doi, ")")
    ),
    citation = str_squish(
      paste(author, year, enquote(title), journal, number, doi)
    )
  )
```

```{r}
#| results: asis

pubs %>%
  filter(category == "peer_reviewed") %>%
  arrange(desc(year)) %>%
  pull(citation) %>%
  make_ordered_list()
```

# Research Projects
```{r}
#| results: asis

pubs %>%
  filter(category == "working") %>%
  mutate(
    citation = str_squish(paste(author, enquote(title), journal))
  ) %>%
  pull(citation) %>%
  make_ordered_list()
```

# Thesis
```{r}
#| results: asis

pubs %>%
  filter(category == "theses") %>%
  pull(citation) %>%
  make_ordered_list()
```

# Presentations
```{r}
presentations <- get_cv_sheet("presentations") %>%
  mutate(across(where(is.character), escape_latex_text)) %>%
  arrange(desc(date)) %>%
  mutate(
    with = ifelse(is.na(with), "", paste0(" With ", with, ".")),
    date = format(as.Date(date), "%B %d, %Y"),
    citation = paste0(
      enquote(title), ".", with, " ",
      host, ", ", location, ". ", date, "."
    )
  )

presentation_counts <- presentations %>%
  count(category) %>%
  mutate(
    category = recode(
      category,
      invited = "Invited Talks",
      conference = "Conference Presentations",
      poster = "Poster Presentations"
    )
  ) %>%
  mutate(
    category = factor(
      category,
      levels = c(
        "Invited Talks",
        "Conference Presentations",
        "Poster Presentations"
      )
    ),
    cite = paste0(category, " (", n, ")")
  ) %>%
  arrange(category) %>%
  pull(cite) %>%
  paste(collapse = ", ")
```

**Total Presentations by Category**: `r presentation_counts`

## A. Invited Talks

```{r}
#| results: asis

presentations %>%
  filter(category == "invited") %>%
  pull(citation) %>%
  make_ordered_list()
```

## B. Conference Presentations
```{r}
#| results: asis

presentations %>%
  filter(category == "conference") %>%
  pull(citation) %>%
  make_ordered_list()
```

## C. Poster Presentations
```{r}
#| results: asis

presentations %>%
  filter(category == "poster") %>%
  pull(citation) %>%
  make_ordered_list()
```

# Honors / Awards
```{r}
awards <- get_cv_sheet("awards") %>%
  mutate(
    date_sort = lubridate::my(date),
    across(where(is.character), escape_latex_text),
    citation = paste0(description, " (", date, ")")
  ) %>%
  arrange(desc(date_sort)) %>%
  select(-date_sort)
```

```{r}
#| results: asis

awards %>%
  pull(citation) %>%
  make_bullet_list()
```

# Teaching Experience
```{r}
classes <- get_cv_sheet("classes") %>%
  mutate(
    semester = recode(
      semester,
      "F20" = "Fall 2020",
      "S21" = "Spring 2021",
      "F21" = "Fall 2021",
      "S22" = "Spring 2022"
    ),
    role = recode(type, assistant = "Teaching Assistant"),
    course = name
  ) %>%
  select(Semester = semester, Role = role, Course = course, Level = level) %>%
  mutate(across(everything(), escape_latex_text))

classes %>%
  kbl(booktabs = TRUE, linesep = "") %>%
  kable_styling(latex_options = c("hold_position", "striped"))
```

# Service and Community Involvement
```{r}
service <- get_cv_sheet("service") %>%
  mutate(across(where(is.character), escape_latex_text)) %>%
  mutate(citation = paste0(activity, " (", dates, ")."))
```

## A. University Service
```{r}
#| results: asis

service %>%
  filter(category == "university") %>%
  pull(citation) %>%
  make_bullet_list()
```

## B. Community / Professional Involvement
```{r}
#| results: asis

service %>%
  filter(category == "professional") %>%
  pull(citation) %>%
  make_bullet_list()
```

# Skills

- Data Analysis: R, SPSS, JASP, jamovi, FlowJo; t-tests, ANOVA, linear regression

- Programming / Reproducible Research: R, Python, SQL, Markdown, Quarto, Git/GitHub

- Molecular & Cellular Techniques: Flow cytometry; DNA/RNA/protein extraction; PCR; gel electrophoresis; ELISA

- Histology & Imaging: Tissue processing, cryosectioning, microtomy, immunohistochemistry, fluorescent immunostaining, fluorescence imaging

- In Vivo / Murine Techniques: IP, IV, and intragastric injections; retro-orbital bleeding; necropsy; spleen and bone marrow harvest; ABSL-2 sterile hood technique

- Research Platforms: IVIS Spectrum, EthoVision XT, Qualtrics, SONA, Microsoft Office, VS Code, Zotero, EndNote, Notion, Obsidian, Canvas

- Research Data Management: R/Quarto dashboards with Plotly and Shiny for workflow tracking and experimental documentation